---
title: "Naturalistic Moral Judgment"
author: "Chelsea Helion & William Mitchell"
format: html
editor: visual
---

## Naturalistic moral judgment task

The goal of this project is to examine what features of nmultimodal narrative stimuli (heretofore called "naturalistic") are associated with fluctuations in moral decision-making. To examine this question, we had participants view a series of video clips taken from popular television shows (e.g., "Mindhunter", "The Night Of"). For each video, participants took one of three perspectives, a detective investigating the case, a friend of the victim, or a friend of the accused (randomly assigned, each condition repeated three times). Task code is available here: [SAN Lab Github.](https://github.com/social-and-affective-neuroscience-lab/PythonScripts/tree/main/Certainty%20Task)

### Load relevant packages and load in data

```{r}
#| label: load-packages/data
#| echo: false
#| include: false
library(tidyverse) # for data wrangling and manipulation
library(skimr) # vaguely nicer version of summary stats
library(scales) # for scaling data (entropy)
library(lme4) # multi-level modeling
library(effects) # quick plots
library(mgcv) # for generalized additive mixed models
library(gratia) # for getting the derivatives of the GAMM models
library(MetBrewer) # palettes for plotting
library(monochromeR) # also palettes for plotting
library(brms) # for hierarchical bayesian models
library(tidybayes) # for bayesian analyses
library(janitor) # for making variable names easier to work with

df_behav <- read_csv("/Users/tua37526/Dropbox/df_cert_behav.csv")

# select variables related to the certainty task
df_behav <- df_behav %>%
  select(
    PID,
    Age,
    Gender,
    Ethnicity,
    Video,
    Time_video,
    Condition,
    Rating,
    IRI_perstake,
    IRI_fantasy,
    IRI_empath,
    IRI_distress,
    DERS_nonaccept,
    DERS_goals,
    DERS_impulse,
    DERS_aware,
    DERS_strategy,
    DERS_clarity,
    emo_Adoration,
    `emo_Aesthetic Appreciation`,
    emo_Amusement,
    emo_Anxiety,
    emo_Awe,
    emo_Boredom,
    emo_Confusion,
    emo_Craving,
    emo_Disgust,
    `emo_Empathic Pain`,
    emo_Entrancement,
    emo_Excitement,
    emo_Fear,
    emo_Horror,
    emo_Interest,
    emo_Joy,
    emo_Romance,
    emo_Sadness,
    `emo_Sexual Desire`,
    emo_Surprise,
    Entropy,
    Comprehend,
    Engaged,
    Influence_Identity,
    Influence_Information,
    Influence_Context,
    Role_Adopt,
    Role_Maintain,
    Role_Influence,
    Complexity,
    Curiosity,
    Intense_Feel,
    Intense_Video
  )

# change some variable types, sort based on time
df_behav$Video <- as.factor(df_behav$Video)
df_behav <-
  df_behav[order(df_behav$Video, df_behav$PID, df_behav$Time_video),]
df_behav$Condition <- as.factor(df_behav$Condition)
df_behav$Video <- as.factor(df_behav$Video)


```

### Generate summary stats for demographic and task features of the dataset

```{r}
#| echo: false

df_behav %>% 
  filter(Time_video == 10,
         Video == "undoingS1E1") %>%
  summarise(mean_age = mean(Age, na.rm = TRUE),
            sd_age = sd(Age, na.rm = TRUE))

df_behav %>%
  filter(Time_video == 1,
         Video == "broadchurchS1E3") %>%
  {table(.$Gender)}


```

### Summary statistics and comparisons across conditions for task-related judgments

Participants indicated the following on seven-point scales: 1) task engagement, 2) task comprehension, 3) emotional intensity, 4) task-related curiosity, 5) evaluations of task complexity, how influential 6) context, 7) information, and 8) character identity was for their judgments. They also indicated the extent to which the role/condition influenced their judgment, how easy the role/condition was to adopt, and how easy the role/condition was to maintain.

```{r}

```
